A sample computation

### 2024-06-27 draft_systoles.tex
Minor misprints correction

\begin{Prop}
	The index of the one centralizer inside the other \emph{does not depend on $p$} and equals $3$.
\end{Prop}
\begin{proof}
As $A$ is equivalent to the cyclic permutation matrix $\pmod p$ it follows $A^3 \in \SLp$.

Thus the smaller centralizer is generated $A^3, \tilde A$
\[
Z_{\SLp}(\tilde A)
= \{ A^{3a} (p A + \Id)^b \mid a, b \in \mathbb{Z} \}
,\] 
and it's clear that the index is $3$.
\end{proof}

>>>>

\begin{Prop}
	The index of the one centralizer inside the other \emph{does not depend on $p$} and equals $3$.
\[
	[Z_{\SL}(\tilde A) : Z_{\SLp}(\tilde A) ] = 3
.\] 
\end{Prop}
\begin{proof}
As $A \pmod p$ is equivalent to the cyclic permutation matrix, it follows that $A^3 \in \SLp$.

Thus the smaller centralizer is generated by $A^3, \tilde A$
\[
Z_{\SLp}(\tilde A)
= \{ A^{3a} (p A + \Id)^b \mid a, b \in \mathbb{Z} \}
,\] 
and it is clear that the index is $3$.
\end{proof}
